---
title: 'Anti-White Discrimination Claims: Primary Analysis'
author: "Elisabeth R Silver"
date: "2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```



```{r}

if (!require("pacman")) install.packages("pacman"); library(pacman)#Load the package manager 
#devtools::install_github("silverer/statstring")
p_load(tidyverse, stats, stringr, effects,
       scales, statstring, Hmisc, interactions,
       cowplot,apaTables,openxlsx,lsmeans,flextable)
filter <- dplyr::filter
select <- dplyr::select
output <- "outputs/"
local_data <- "data/"
box_data <- "../../Library/CloudStorage/Box-Box/EEOC data/"
```

# Merge EEOC and Census data

Read in the EEOC data and merge with Census data (note: white_unemployment_pop.csv comes from the Python notebook `Get Census Data with Unemployment.ipynb`. It contains population information about race and unemployment, both in total and for white people. This isn't generated in R since I needed to get estimates from both the data profiles and the subject tables.)

```{r}
grpd_demog_county <- read.csv(paste0(box_data,"agg_claim_info_county_w_retal_v1.csv"))
#this should be 0
#nrow(grpd_demog_county[!is.na(grpd_demog_county$fixed_fip),])
grpd_demog_county <- grpd_demog_county[!is.na(grpd_demog_county$fixed_fip),]


grpd_demog_county$fixed_fip <- str_pad(grpd_demog_county$fixed_fip, 
                                       width = 5, side = "left",
                                       pad = "0")
#https://www2.census.gov/geo/maps/general_ref/us_base/stco2010/USstcou2010_wallmap.pdf
acs_data <- read.csv(paste0(box_data, "white_unemployment_pop.csv"))
acs_data["fixed_fip"] <- str_pad(acs_data$fixed_fip, width = 5, side = "left",
                                 pad = "0")
acs_data["in_df"] <- acs_data$fixed_fip %in% grpd_demog_county$fixed_fip
grpd_demog_county <- left_join(grpd_demog_county, acs_data, by = "fixed_fip")

```


Save the merged dataset:

```{r}
write.csv(grpd_demog_county, paste0(box_data,
                                    "agg_claim_info_county_w_census_w_retal_v1.csv"))
```


# Read in merged EEOC Census data file and run analyses

Read in the dataset and get table 1:

```{r, results = "asis"}

grpd_demog_county <- read.csv(paste0(box_data,
                                    "agg_claim_info_county_w_census_w_retal_v1.csv"))
grpd_demog_county$fixed_fip <- str_pad(grpd_demog_county$fixed_fip, width = 5, side = "left",
                                       pad="0")

cat("total complaints (w retal): ")
cat(number(sum(grpd_demog_county$n.complaints), big.mark = ","))
cat("  \nexcluded bc retaliation: ")
no.retal.comps <- sum(grpd_demog_county$n.complaints.noretal)
cat(number(sum(grpd_demog_county$n.complaints)-no.retal.comps,big.mark = ","))
cat("  \nfailed geocode (without retal) ")
nfail <- sum(grpd_demog_county$n.complaints.noretal[grpd_demog_county$fixed_fip=="FAILED"])
cat(nfail)
cat("  \n")
cat(percent(nfail/no.retal.comps, accuracy = .01))
grpd_demog_county <- grpd_demog_county[grpd_demog_county$fixed_fip!= "FAILED",]

before_exclude <- nrow(grpd_demog_county)
no_comp_df <- grpd_demog_county[grpd_demog_county$n.complaints.noretal==0,]
cat("  \naverage population of counties without any complaints: ")
cat(mean(no_comp_df$total_pop, na.rm=T))
cat("  \nrange of population for counties without any complaints: ")
cat(range(no_comp_df$total_pop))
cat("  \nno complaints in county: ")
cat(nrow(no_comp_df))
grpd_demog_county<-grpd_demog_county[grpd_demog_county$n.complaints.noretal>0,]

no_cons <-  grpd_demog_county %>% 
  filter(is.na(mrp_ideology_mean))
grpd_demog_county <- grpd_demog_county %>% 
  filter(!is.na(mrp_ideology_mean))
cat("  \nnumber of counties without conservatism score: ")
cat(nrow(no_cons))
cat("  \n")
cat("Final num. of non-retaliation complaints: ")
cat(sum(grpd_demog_county$n.complaints.noretal))
cat("  \nFinal num. of counties: ")
cat(nrow(grpd_demog_county))

cat("  \nnum complaints no retal: ")
cat(sum(grpd_demog_county$n.complaints.noretal))
cat("  \nnum anti-white discrimination complaints: ")
cat(sum(grpd_demog_county$n.white))
cat("  \npercent anti-white discrimination complaints no retal: ")
cat(sum(grpd_demog_county$n.white)/sum(grpd_demog_county$n.complaints.noretal))

grpd_demog_county$fixed_fip <- str_pad(grpd_demog_county$fixed_fip, 
                                       width = 5, side = "left",
                                       pad = "0")

#grpd_demog_county[grpd_demog_county$fixed_fip=="11001",] #double-check that DC is included
grpd_demog_county["prop_white_comp"] <- grpd_demog_county$n.white/grpd_demog_county$n.complaints.noretal

grpd_demog_county$prop_white_comp[grpd_demog_county$n.white==0] <- 0

grpd_demog_county["sqrt_prop_white"] <- sqrt(grpd_demog_county$prop_white_comp)
grpd_demog_county["acs_nonwhite_prop"] <- (100 - grpd_demog_county$percent_white)/100
grpd_demog_county["acs_unemploy_white"] <- grpd_demog_county$unemploy_white/100

```

```{r}
#create a pretty correlation table
graph_county <- grpd_demog_county %>% 
  dplyr::select(prop_white_comp,
                acs_nonwhite_prop,
                acs_unemploy_white,
                mrp_ideology_mean) %>% 
  dplyr::mutate(prop_white_comp = 100 * prop_white_comp,
                acs_nonwhite_prop = 100 * acs_nonwhite_prop,
                acs_unemploy_white = 100 * acs_unemploy_white) %>% 
  dplyr::rename(`Anti-white claim prevalence` = prop_white_comp,
                `Percent POC` = acs_nonwhite_prop,
                `White unemployment` = acs_unemploy_white,
                `Conservatism` = mrp_ideology_mean)
ms <- graph_county %>% 
  summarise(across(everything(),
                   mean)) %>% 
  pivot_longer(everything()) %>% 
  rename(Mean = value)
sds <- graph_county %>% 
  summarise(across(everything(),
                   sd)) %>% 
  pivot_longer(everything()) %>% 
  rename(`Std. Dev` = value) 
rg <- graph_county %>% 
  summarise(across(everything(),
                   range)) %>% 
  mutate(desig = c("min", "max")) %>% 
  pivot_longer(!desig) %>% 
  pivot_wider(id_cols = name, values_from=value, names_from=desig) %>% 
  mutate(Range = str_c(number(min, accuracy = .1), ", ", number(max, accuracy = .1)))
descriptives <- cbind(ms, sds %>% 
                        select(-name), 
                      rg %>% 
                        select(-name))
descriptives <- descriptives %>% 
  mutate(`M (SD)` = str_c(number(Mean, accuracy = .1), 
                          " (", 
                          number(`Std. Dev`, accuracy=.1), ")")) %>% 
  select(all_of(c("name", "M (SD)", "Range")))

cor.res <- data.frame(apa.cor.table(as.matrix(graph_county))$table.body)
cor.res <- cor.res %>% 
  filter(str_starts(Variable, "\\d+[.]")) %>% 
  mutate(name = str_remove(Variable, "\\d+[.] ")) %>% 
  left_join(descriptives, by="name") %>% 
  select(-name, -M, -SD) %>% 
  select(Variable, `M (SD)`, Range, X1, X2, X3) %>% 
  rename(`1` = X1, `2` = X2, `3` = X3)

f <- cor.res %>% 
  flextable() %>% 
  set_header_labels(colnames(cor.res)) %>% 
  align(1:nrow(cor.res), 2:ncol(cor.res), align = "center")%>% 
  bold(c(1), 1:ncol(cor.res), part = "header") %>% 
  add_footer_lines(paste0("Note. N = ",
                          scales::number(nrow(graph_county), big.mark=",", accuracy = 1),
                          " counties. POC indicates people of color, M indicates mean, SD indicates standard deviation. ** indicates p < .01."))
f
write.csv(cor.res, paste0(output, "correlation_descriptives_v1.csv"))
```

Compare normality of residuals for transformed and untransformed outcome variable:

```{r}
m0.ut <- lm(prop_white_comp~acs_nonwhite_prop+mrp_ideology_mean+acs_unemploy_white,
            data=grpd_demog_county)
resid.ut <- m0.ut$residuals
m1 <- lm(sqrt_prop_white~acs_nonwhite_prop+mrp_ideology_mean+acs_unemploy_white,
            data=grpd_demog_county)
resid.m1 <- m1$residuals

resids <- data.frame(resid.ut,
                     resid.m1) %>% 
  pivot_longer(everything())

resid.plots <- resids %>%
  mutate(Outcome = recode(name, 
                       resid.m1 = "Transformed", 
                       resid.ut = "Untransformed")) %>% 
  ggplot(aes(value))+
  geom_histogram(binwidth = .1)+
  facet_wrap(vars(Outcome))+
  labs(x = "Residuals", y = "Frequency", 
       title = "Residual Distribution: Transformed vs. Untransformed Outcome")+
  theme_bw()+
  theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
        strip.text.x = element_text(size=12),
        text = element_text(family="Times"),
          axis.text=element_text(size=12),
          title = element_text(size = 10),
        legend.text = element_text(size=12))
save_plot(paste0(output, "residual_comparison.png"), resid.plots)
```



Run the regression analyses:

```{r}

m2 <- lm(sqrt_prop_white~acs_nonwhite_prop*mrp_ideology_mean+acs_unemploy_white,
            data=grpd_demog_county)
summary(m2)

m3 <- lm(sqrt_prop_white~acs_nonwhite_prop*mrp_ideology_mean*acs_unemploy_white,
            data=grpd_demog_county)
summary(m3)
```


```{r}
#conduct slope difference tests
mrp_levels <- c((mean(grpd_demog_county$mrp_ideology_mean,
                                                                na.rm=T)-
                                                             sd(grpd_demog_county$mrp_ideology_mean,
                                                                na.rm = T)),
                                                          (mean(grpd_demog_county$mrp_ideology_mean,
                                                                na.rm=T)+
                                                             sd(grpd_demog_county$mrp_ideology_mean,
                                                                na.rm = T)))
div_levels <- c((mean(grpd_demog_county$acs_nonwhite_prop)-
                                                              sd(grpd_demog_county$acs_nonwhite_prop)),
                                                           (mean(grpd_demog_county$acs_nonwhite_prop)+
                                                              sd(grpd_demog_county$acs_nonwhite_prop)))
unemp_levels <- c((mean(grpd_demog_county$acs_unemploy_white)-
                                                              sd(grpd_demog_county$acs_unemploy_white)),
                                                           (mean(grpd_demog_county$acs_unemploy_white)+
                                                              sd(grpd_demog_county$acs_unemploy_white)))
pair.df <- data.frame()
m.lst <- lstrends(m2, ~mrp_ideology_mean,
                  var = "acs_nonwhite_prop",at = list(mrp_ideology_mean=mrp_levels))
print(pairs(m.lst))
tmp.pairs <- data.frame(pairs(m.lst))
tmp.pairs <- tmp.pairs %>% 
  mutate(acs_unemploy_white = NA_character_) %>% 
  select(contrast, acs_unemploy_white,estimate,SE,df,t.ratio,p.value)

m.lst <- lstrends(m3, ~mrp_ideology_mean|acs_unemploy_white,
                  var = "acs_nonwhite_prop",at = list(mrp_ideology_mean=mrp_levels,
                                                      acs_unemploy_white=unemp_levels))
print(pairs(m.lst))
pair.df <- rbind(tmp.pairs,data.frame(pairs(m.lst)))
```


Format and save regression outputs: 

```{r}

reg_fmt <- read.csv(paste0(local_data,"regression_format.csv"))
format_regression_table <- function(models){
  tracker = 1
  for(m in models){
    #print(tracker)
    tmp_res = summary(m)
    tmp_coef = data.frame(tmp_res$coefficients)
    tmp_coef[,1] = number(tmp_coef[,1],accuracy = .01)#beta
    tmp_coef[,2] = number(tmp_coef[,2], accuracy = .01)#SE beta
    tmp_coef[,4] = sapply(tmp_coef[,4], statstring::format_sig_stars)#p-val
    tmp_coef[,1] = paste0(tmp_coef[,1], tmp_coef[,4])
    tmp_coef["Predictor"] = rownames(tmp_coef)
    mnum = paste0("model", tracker, "_")
    colnames(tmp_coef) = c(paste0(mnum, c("b", "se_b", "t", "p")), "Predictor")
    tmp_coef = tmp_coef %>% 
      select(Predictor, ends_with("_b"), ends_with("se_b"))
    reg_fmt = left_join(reg_fmt, tmp_coef, by = "Predictor")
    #print(number(statstring::extract_r2(m),accuracy = .001))
    reg_fmt[reg_fmt$Predictor == "R2", paste0(mnum, "se_b")] = number(tmp_res$adj.r.squared,
                                                                       accuracy = .001)
    if(tracker > 1){
      mod_aov = anova(models[[tracker - 1]], models[[tracker]])
      reg_fmt[reg_fmt$Predictor == "Change in R2", 
              paste0(mnum, "se_b")] <- paste0(number(mod_aov$`F`[2], accuracy =.01),
                                              format_sig_stars(mod_aov$`Pr(>F)`[2]))
    }
    tracker = tracker + 1
  }
  reg_fmt[is.na(reg_fmt)] = "-"
  return(reg_fmt)
}

modlist <- list(m1,m2,m3)
reg_out <- format_regression_table(modlist)

write.xlsx(reg_out, paste0(output, "regression_outs_no_retal_v1.xlsx"),overwrite = T)

```

```{r}
#create pretty regression table
reg_out <- reg_out %>% 
  select(-any_of(c("Predictor")))
header_1 <- c("Predictor"=1, 
              "Model 1"=2,
              "Model 2"=2,
              "Model 3"=2)
header_2 <-c("",rep(c("b", "SE b"), 3))
head_list <- c(header_2)
names(head_list) <- colnames(reg_out)

f <- reg_out %>%  
  flextable() %>% 
  set_header_labels(values=head_list) %>% 
  add_header_row(values=names(header_1),
                 colwidths = c(1, rep(2,length(header_1)-1))) %>% 
  align(1:nrow(reg_out), 2:ncol(reg_out),align = "center") %>%  
  align(c(1), 2:ncol(reg_out),align = "center",part="header") %>%  
  bold(c(1), 1:ncol(reg_out), part = "header") %>% 
  italic(c(2), 1:ncol(reg_out), part = "header") %>% 
  add_footer_lines(paste0("Note. N = ",
                          number(nrow(graph_county), big.mark=",", accuracy = 1),
                   " counties. The criterion has been square-root transformed to improve the normality of residuals. b represents the unstandardized regression weight, SE indicates standard error. * indicates p < .05. ** indicates p < .01. *** indicates p < .001"))
f
```


Examine the interaction:

H2: two-way between conservatism and racial diversity:


```{r}
jn_h2 <- sim_slopes(m2, pred=acs_nonwhite_prop,
                      modx=mrp_ideology_mean,
                      modx.values = "plus-minus",
                      confint=T,jnplot=T)
jn_h2
```

H3 interaction between diversity, conservatism, and white unemployment:

```{r}

jn_h3 <- sim_slopes(m3, pred=acs_nonwhite_prop,
                      modx=mrp_ideology_mean,
                      modx.values = "plus-minus",
                      mod2=acs_unemploy_white,
                      mod2.values = "plus-minus",
                      confint=T,jnplot=T)
jn_h3
```


```{r}
#create +/- 1 SD of mean for plots
cons_levels <- c((mean(grpd_demog_county$mrp_ideology_mean)-
                    sd(grpd_demog_county$mrp_ideology_mean)),
                 mean(grpd_demog_county$mrp_ideology_mean),
                 (mean(grpd_demog_county$mrp_ideology_mean)+
                    sd(grpd_demog_county$mrp_ideology_mean)))
unemploy_levels <- c((mean(grpd_demog_county$acs_unemploy_white)-
                    sd(grpd_demog_county$acs_unemploy_white)),
                 mean(grpd_demog_county$acs_unemploy_white),
                 (mean(grpd_demog_county$acs_unemploy_white)+
                    sd(grpd_demog_county$acs_unemploy_white)))
div_levels <- c((mean(grpd_demog_county$acs_nonwhite_prop)-
                    sd(grpd_demog_county$acs_nonwhite_prop)),
                 mean(grpd_demog_county$acs_nonwhite_prop),
                 (mean(grpd_demog_county$acs_nonwhite_prop)+
                    sd(grpd_demog_county$acs_nonwhite_prop)))
```

Plot H1

```{r}
intrxn.sd <- effect(c("acs_nonwhite_prop"),
               mod = m1)

intrxn.sd <- as.data.frame(intrxn.sd)
m1.sum <- data.frame(summary(m1)$coefficients)
slope_lab <- paste0("b = ", number(m1.sum$Estimate[2],accuracy = .01),
                    format_sig_stars(m1.sum$Pr...t..[2]),
                    " SE = ", number(m1.sum$Std..Error[2],accuracy = .01))
# Plot this bad boy!
h1_plot<-
  intrxn.sd %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit))+
      geom_line(size=1)+ #Can adjust the thickness of your lines
      geom_point(size=2)+ #Can adjust the size of your points
      geom_ribbon(aes(ymin=fit-se, ymax=fit+se),fill="gray",alpha=.4)+ #Can adjust your error bars
      labs(y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("Model 1: Anti-White Claim Prevalence by Racial Diversity")+ #Title
  theme_bw()+
  xlim(left = 0,
        right = .5)+
  ylim(bottom=.05,
       top = .2)+
  geom_text(aes(x = .25, y = .16, label=slope_lab),size=4,family="Times")+
  theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12))

save_plot(paste0(output, "h1_plot_v2.png"), h1_plot)
h1_plot
```

Plot H2: Claim prevalence by racial diversity and conservatism

```{r}

intrxn.sd <- effect(c("acs_nonwhite_prop*mrp_ideology_mean"),
               mod = m2, 
               xlevels = list(mrp_ideology_mean=c(cons_levels[1],cons_levels[3]),
                              acs_nonwhite_prop=c(div_levels[1],div_levels[3])))

intrxn.sd <- as.data.frame(intrxn.sd)
mod.labs <- c("-1 SD", "+ 1 SD")
# Create factors of the different variables in your interaction 
intrxn.sd$mrp_ideology_mean<-factor(intrxn.sd$mrp_ideology_mean,
                      levels=c(cons_levels[1],cons_levels[3]),
                      labels=c("Low Conservatism", "High Conservatism"))
intrxn.sd$mrp_ideology_mean_rev <- factor(intrxn.sd$mrp_ideology_mean, 
                                      levels = rev(levels(intrxn.sd$mrp_ideology_mean)))
format_slope_text <- function(slope.df){
  new.list = rep("", nrow(slope.df))
  for(i in 1:nrow(slope.df)){
    new.list[i] = paste0("b = ", number(slope.df$`Est.`[i],
                                        accuracy = .01),
                         format_sig_stars(slope.df$p[i]),
                         " SE = ", number(slope.df$`S.E.`[i],
                                             accuracy = .01))
  }
  return(new.list)
}
m2.slopes <- jn_h2$slopes
m2.slopes["text"] <- format_slope_text(m2.slopes)

m2.slopes["x"] <- c(.375, .275)
m2.slopes["y"] <- c(.14,.175)
m2.slopes["mrp_ideology_mean"] <-c("Low Conservatism", "High Conservatism")
joined <- left_join(intrxn.sd, m2.slopes, by = "mrp_ideology_mean")
# Plot this bad boy!
h2_plot<-
  joined %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit, 
             group=mrp_ideology_mean))+
      geom_line(size=1, aes(color=mrp_ideology_mean))+ #Can adjust the thickness of your lines
      geom_point(aes(colour = mrp_ideology_mean), size=2)+ #Can adjust the size of your points
      geom_ribbon(aes(ymin=fit-se, ymax=fit+se),fill="gray",alpha=.2)+ #Can adjust your error bars
      labs(color = "Conservatism", y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("Model 2: Anti-White Claim Prevalence by\n Racial Diversity and Conservatism")+ #Title
  theme_bw()+
  scale_color_manual(values=c("#A52B2B", "#2B5EA5"))+
  geom_text(aes(x= x, y = y, label = text,
                color=mrp_ideology_mean),
            family = "Times",
            size=4,
            show.legend = F)+
   xlim(left = 0,
        right = .5)+ 
  ylim(bottom = .05,
       top = .2)+
  theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          legend.position="top",
        legend.title = element_blank(),
        text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12),
        legend.text = element_text(size=10))
h2_plot 
save_plot(paste0(output, "h2_plot_v2.png"), h2_plot)
#save_plot("moderation_v1.png", Plot.SD)
#Plot.SD
```

Plot the 2-way diversity x conservatism interaction separately for counties with low white unemployment and counties with high white unemployment.

Low white unemployment:

```{r}

intrxn.sd <- effect(c("acs_nonwhite_prop*mrp_ideology_mean*acs_unemploy_white"),
               mod = m3, 
               xlevels = list(mrp_ideology_mean=c(cons_levels[1],cons_levels[3]),
                              acs_unemploy_white=c(unemploy_levels[1], unemploy_levels[3]),
                              acs_nonwhite_prop=c(div_levels[1],div_levels[3])))

intrxn.sd <- as.data.frame(intrxn.sd)
mod.labs <- c("-1 SD", "+ 1 SD")
# Create factors of the different variables in your interaction 
intrxn.sd$mrp_ideology_mean<-factor(intrxn.sd$mrp_ideology_mean,
                      levels=c(cons_levels[1],cons_levels[3]),
                      labels=c("Low Conservatism", "High Conservatism"))
intrxn.sd$mrp_ideology_mean_rev <- factor(intrxn.sd$mrp_ideology_mean, 
                                      levels = rev(levels(intrxn.sd$mrp_ideology_mean)))

intrxn.sd$acs_unemploy_white<-factor(intrxn.sd$acs_unemploy_white,
                      levels=c(unemploy_levels[1], unemploy_levels[3]),
                      labels=c("Low White Unemploy", "High White Unemploy"))
intrxn.sd$acs_unemploy_white_rev <- factor(intrxn.sd$acs_unemploy_white, 
                                      levels = rev(levels(intrxn.sd$acs_unemploy_white)))

m3.slopes <- data.frame(jn_h3$slopes[[1]])
m3.slopes["acs_unemploy_white"] <- "Low White Unemploy"
tmp.slopes <- data.frame(jn_h3$slopes[[2]])
tmp.slopes["acs_unemploy_white"] <- "High White Unemploy"
m3.slopes <- rbind(m3.slopes, tmp.slopes)
m3.slopes["mrp_ideology_mean"] <- c("Low Conservatism", "High Conservatism",
                                    "Low Conservatism", "High Conservatism")
m3.slopes["text"] <- format_slope_text(m3.slopes)
#low white unemploy, low cons; low white unemploy, high cons; 
#high white unemploy low cons; high white unemploy, high cons
m3.slopes["x"] <- c(.15, .325,.348,.153)
m3.slopes["y"] <- c(.153,.1,.119,.175)

joined <- left_join(intrxn.sd, m3.slopes, by = c("mrp_ideology_mean", "acs_unemploy_white"))
joined$acs_unemploy_white <- factor(joined$acs_unemploy_white,
                                        levels = c("Low White Unemploy","High White Unemploy"))
# Plot this bad boy!
Plot.SD<-
  joined %>% 
  filter(acs_unemploy_white_rev=="Low White Unemploy") %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit, 
             group=mrp_ideology_mean_rev))+
      geom_line(size=1, aes(color=mrp_ideology_mean_rev))+ 
      geom_point(aes(colour = mrp_ideology_mean_rev), size=2)+ 
      #facet_wrap(~acs_unemploy_white)+
      geom_ribbon(aes(ymin=fit-se, ymax=fit+se),
                  fill="gray",alpha=.2)+ 
      labs(color = "Conservatism", y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("LOW White Unemployment: Anti-White Claim Prevalence by\nRacial Diversity and Conservatism")+ #Title
  theme_bw()+
  geom_text(aes(x= x, y = y, label = text,
                color=mrp_ideology_mean),
            show.legend = F,family="Times",size=4)+
      theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          legend.position="top",
        legend.title = element_blank(),
        legend.text = element_text(size=9),
        text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12),
        strip.text.x = element_text(size = 10))+ 
   xlim(left = 0,
        right = .5)+
  ylim(bottom = .05,
       top = .2)+
  scale_color_manual(values=c("#A52B2B", "#2B5EA5"))
#save_plot("h3_plot.png", Plot.SD)
save_plot(paste0(output, "low_white_unemploy_v1.png"), Plot.SD)
#save_plot(paste0(output, "h3_plot_v1.png"), Plot.SD)
Plot.SD
```

High white unemployment:

```{r}
Plot.SD<-
  joined %>% 
  filter(acs_unemploy_white_rev=="High White Unemploy") %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit, 
             group=mrp_ideology_mean_rev))+
      geom_line(size=1, aes(color=mrp_ideology_mean_rev))+ 
      geom_point(aes(colour = mrp_ideology_mean_rev), size=2)+ 
      #facet_wrap(~acs_unemploy_white)+
      geom_ribbon(aes(ymin=fit-se, ymax=fit+se),
                  fill="gray",alpha=.2)+ 
      labs(color = "Conservatism", y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("HIGH White Unemployment: Anti-White Claim Prevalence by\nRacial Diversity and Conservatism")+ #Title
  theme_bw()+
  geom_text(aes(x= x, y = y, label = text,
                color=mrp_ideology_mean),
            show.legend = F,family="Times",size=4)+
      theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          legend.position="top",
        legend.title = element_blank(),
        legend.text = element_text(size=9),
        text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12),
        strip.text.x = element_text(size = 10))+ 
   xlim(left = 0,
        right = .5)+
  ylim(bottom = .05,
       top = .22)+
  scale_color_manual(values=c("#A52B2B", "#2B5EA5"))
Plot.SD
#save_plot("h3_plot.png", Plot.SD)
save_plot(paste0(output, "high_white_unemploy_v1.png"), Plot.SD)
```


Plot the 3-way interaction with a pretty title:

```{r}
# Plot this bad boy!
Plot.SD<-
  joined %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit, 
             group=mrp_ideology_mean_rev))+
      geom_line(size=1, aes(color=mrp_ideology_mean_rev))+ 
      geom_point(aes(colour = mrp_ideology_mean_rev), size=2)+ 
      facet_wrap(~acs_unemploy_white)+
      geom_ribbon(aes(ymin=fit-se, ymax=fit+se),
                  fill="gray",alpha=.2)+ 
      labs(color = "Conservatism", y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("Anti-White Claim Prevalence by County\nRacial Diversity, Conservatism, and White Unemployment")+ #Title
  theme_bw()+
  geom_text(aes(x= x, y = y, label = text,
                color=mrp_ideology_mean),
            show.legend = F,family="Times",size=4)+
      theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          legend.position="top",
        legend.title = element_blank(),
        legend.text = element_text(size=9),
        text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12),
        strip.text.x = element_text(size = 10))+ 
   xlim(left = 0,
        right = .5)+
  scale_color_manual(values=c("#A52B2B", "#2B5EA5"))
#save_plot("h3_plot.png", Plot.SD)
save_plot(paste0(output, "h3_plot_paper_v1.png"), Plot.SD)
Plot.SD
```

Plot the 3-way interaction in black and white:

```{r}

intrxn.sd <- effect(c("acs_nonwhite_prop*mrp_ideology_mean*acs_unemploy_white"),
               mod = m3, 
               xlevels = list(mrp_ideology_mean=c(cons_levels[1],cons_levels[3]),
                              acs_unemploy_white=c(unemploy_levels[1], unemploy_levels[3]),
                              acs_nonwhite_prop=c(div_levels[1],div_levels[3])))

intrxn.sd <- as.data.frame(intrxn.sd)
mod.labs <- c("-1 SD", "+ 1 SD")
# Create factors of the different variables in your interaction 
intrxn.sd$mrp_ideology_mean<-factor(intrxn.sd$mrp_ideology_mean,
                      levels=c(cons_levels[1],cons_levels[3]),
                      labels=c("Low Conservatism", "High Conservatism"))
intrxn.sd$mrp_ideology_mean_rev <- factor(intrxn.sd$mrp_ideology_mean, 
                                      levels = rev(levels(intrxn.sd$mrp_ideology_mean)))

intrxn.sd$acs_unemploy_white<-factor(intrxn.sd$acs_unemploy_white,
                      levels=c(unemploy_levels[1], unemploy_levels[3]),
                      labels=c("Low White Unemploy", "High White Unemploy"))
intrxn.sd$acs_unemploy_white_rev <- factor(intrxn.sd$acs_unemploy_white, 
                                      levels = rev(levels(intrxn.sd$acs_unemploy_white)))

m3.slopes <- data.frame(jn_h3$slopes[[1]])
m3.slopes["acs_unemploy_white"] <- "Low White Unemploy"
tmp.slopes <- data.frame(jn_h3$slopes[[2]])
tmp.slopes["acs_unemploy_white"] <- "High White Unemploy"
m3.slopes <- rbind(m3.slopes, tmp.slopes)
m3.slopes["mrp_ideology_mean"] <- c("Low Conservatism", "High Conservatism",
                                    "Low Conservatism", "High Conservatism")
m3.slopes["text"] <- format_slope_text(m3.slopes)
#low white unemploy, low cons; low white unemploy, high cons; 
#high white unemploy low cons; high white unemploy, high cons
m3.slopes["x"] <- c(.15, .325,.356,.153)
m3.slopes["y"] <- c(.153,.1,.12,.175)

joined <- left_join(intrxn.sd, m3.slopes, by = c("mrp_ideology_mean", "acs_unemploy_white"))
joined$acs_unemploy_white <- factor(joined$acs_unemploy_white,
                                        levels = c("Low White Unemploy","High White Unemploy"))

# Plot this bad boy!
Plot.SD<-
  joined %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit, 
             group=mrp_ideology_mean_rev))+
      geom_line(size=1, aes(linetype=mrp_ideology_mean_rev))+ 
      geom_point(size=2)+ 
      facet_wrap(~acs_unemploy_white)+
      geom_ribbon(aes(ymin=fit-se, ymax=fit+se),
                  fill="gray",alpha=.2)+ 
      labs(color = "Conservatism", y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("Anti-White Claim Prevalence by County\nRacial Diversity, Conservatism, and White Unemployment")+ #Title
  theme_bw()+
  geom_text(aes(x= x, y = y, label = text),
            show.legend = F,family="Times",size=4)+
      theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          legend.position="top",
        legend.title = element_blank(),
        legend.text = element_text(size=9),
        text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12),
        strip.text.x = element_text(size = 10))+ 
   xlim(left = 0,
        right = .5)

save_plot(paste0(output, "h3_plot_paper_bw.png"), Plot.SD)
#save as .tiff
save_plot(paste0(output, "h3_plot_paper_bw.tiff"), Plot.SD)
Plot.SD
```

