---
title: 'Anti-White Discrimination Claims: Primary Analysis'
author: "Elisabeth R Silver"
date: "2024"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```



```{r}

if (!require("pacman")) install.packages("pacman"); library(pacman)#Load the package manager 
#devtools::install_github("silverer/statstring")
p_load(tidyverse, stats, effects,haven,apaTables,
       scales, statstring, Hmisc, interactions,
       cowplot,apaTables,openxlsx,lsmeans,flextable)
filter <- dplyr::filter
select <- dplyr::select
output <- "outputs/"
local_data <- "data/"
box_data <- "../../Library/CloudStorage/Box-Box/EEOC data/"
```

# Merge EEOC and Census data

Read in the EEOC data and merge with Census data (note: `emp_pop_data_05_14.csv` comes from the Python notebook `Get Census Data with Unemployment.ipynb`)

```{r}
grpd_demog_county <- read.csv(paste0(box_data,"agg_claim_info_county_w_retal_v1.csv"))
grpd_demog_county$n.poc.comp <- grpd_demog_county$n.race - grpd_demog_county$n.white
grpd_demog_county <- grpd_demog_county[!is.na(grpd_demog_county$fixed_fip),]


grpd_demog_county$fixed_fip <- str_pad(grpd_demog_county$fixed_fip, 
                                       width = 5, side = "left",
                                       pad = "0")
#https://www2.census.gov/geo/maps/general_ref/us_base/stco2010/USstcou2010_wallmap.pdf
#https://www2.census.gov/geo/maps/general_ref/us_base/stco2010/USstcou2010_wallmap.pdf
acs_data <- read.csv(paste0(box_data, "emp_pop_data_05_14.csv"))
acs_data <- acs_data %>% 
  select(state, county, ends_with("1014")) %>% 
  rename_with(~str_remove(.x, "[_]1014"), ends_with("1014")) %>% 
  mutate(fixed_fip = str_c(str_pad(state, width=2,pad="0",side="left"),
                           str_pad(county, width=3,pad="0",side="left")))
#emp_pop_data_05_14.csv
# acs_data["fixed_fip"] <- str_pad(acs_data$fixed_fip, width = 5, side = "left",
#                                  pad = "0")
acs_data["in_df"] <- acs_data$fixed_fip %in% grpd_demog_county$fixed_fip
#table(acs_data$in_df)
#acs_data %>% filter(in_df==F)#these are mostly in PR
grpd_demog_county <- left_join(grpd_demog_county, acs_data, by = "fixed_fip")

```

```{r}
ideol <- read_dta(paste0(box_data, "aip_counties_ideology_v2022a.dta"))
ideol["fixed_fip"] <- str_pad(ideol$county_fips, width = 5, side = "left",
                                  pad = "0")
ideol <- ideol %>% 
  filter(survey_period == "2004-2011")
#there are some "duplicates" that actually have the same information for all columns except democratic vote share.
dups <- ideol %>% 
  dplyr::group_by(fixed_fip, survey_period) %>%
  dplyr::summarise(n = dplyr::n(), .groups = "drop") %>%
  dplyr::filter(n > 1L) 

dup.insp <- ideol %>% filter(fixed_fip %in% dups$fixed_fip)
#View(dup.insp)

ideol <- ideol %>% 
  group_by(fixed_fip) %>% 
  filter(!duplicated(survey_period)) %>% #remove duplicate records
  ungroup()
```

```{r}
grpd_demog_county <- left_join(grpd_demog_county, ideol, by= "fixed_fip")
```


# Read in merged EEOC Census data file and run analyses

Get descriptive information:

```{r}
orig.df <- grpd_demog_county
```


```{r, results = "asis"}

cat("total complaints (w retal): ")
cat(number(sum(grpd_demog_county$n.complaints), big.mark = ","))
cat("  \nexcluded bc retaliation: ")
no.retal.comps <- sum(grpd_demog_county$n.complaints.noretal)
cat(number(sum(grpd_demog_county$n.complaints)-no.retal.comps,big.mark = ","))
cat("  \nfailed geocode (without retal) ")
nfail <- sum(grpd_demog_county$n.complaints.noretal[grpd_demog_county$fixed_fip=="FAILED"])
cat(nfail)
cat("  \n")
cat(percent(nfail/no.retal.comps, accuracy = .01))
grpd_demog_county <- grpd_demog_county[grpd_demog_county$fixed_fip!= "FAILED",]

before_exclude <- nrow(grpd_demog_county)
no_comp_df <- grpd_demog_county[grpd_demog_county$n.complaints.noretal==0,]
cat("  \naverage population of counties without any complaints: ")
cat(mean(no_comp_df$total_pop, na.rm=T))
cat("  \nrange of population for counties without any complaints: ")
cat(range(no_comp_df$total_pop))
cat("  \nno complaints in county: ")
cat(nrow(no_comp_df))
#temporary dataset for robustness check including 0 claim counties
grpd_rbst <- grpd_demog_county %>% 
  filter(!is.na(mrp_ideology))
grpd_demog_county<-grpd_demog_county[grpd_demog_county$n.complaints.noretal>0,]

no_cons <-  grpd_demog_county %>% 
  filter(is.na(mrp_ideology))
grpd_demog_county <- grpd_demog_county %>% 
  filter(!is.na(mrp_ideology))
cat("  \nnumber of counties without conservatism score: ")
cat(nrow(no_cons))
cat("  \nnumber of cases without conservatism score: ")
cat(sum(no_cons$n.complaints.noretal, na.rm=T))
cat("  \n")
cat("Final num. of non-retaliation complaints: ")
cat(sum(grpd_demog_county$n.complaints.noretal))
cat("  \nFinal num. of counties: ")
cat(nrow(grpd_demog_county))

cat("  \nnum complaints no retal: ")
cat(sum(grpd_demog_county$n.complaints.noretal))
cat("  \nnum anti-white discrimination complaints: ")
cat(sum(grpd_demog_county$n.white))
cat("  \npercent anti-white discrimination complaints no retal: ")
cat(sum(grpd_demog_county$n.white)/sum(grpd_demog_county$n.complaints.noretal))

grpd_demog_county["prop_white_comp"] <- (grpd_demog_county$n.white/grpd_demog_county$n.complaints.noretal)*100
grpd_demog_county$prop_white_comp[grpd_demog_county$n.white==0] <- 0

grpd_rbst["prop_white_comp"] <- (grpd_rbst$n.white/grpd_rbst$n.complaints.noretal)*100
grpd_rbst$prop_white_comp[grpd_rbst$n.white==0] <- 0

grpd_demog_county["sqrt_prop_white"] <- sqrt(grpd_demog_county$prop_white_comp)

```


```{r}
grpd_demog_county <- grpd_demog_county %>% 
  mutate(acs_nonwhite_prop=percent_poc,
         acs_unemploy_white=white_unemp_rate)
grpd_rbst <- grpd_rbst %>% 
  mutate(acs_nonwhite_prop=percent_poc,
         acs_unemploy_white=white_unemp_rate)
```


```{r}
grpd_demog_county$log_total_pop <- log(grpd_demog_county$total_pop)
```


```{r}
#create a pretty correlation table
graph_county <- grpd_demog_county %>% 
  dplyr::select(prop_white_comp,
                acs_nonwhite_prop,
                acs_unemploy_white,
                mrp_ideology,
                log_total_pop) %>% 
  dplyr::rename(`Anti-white claim prevalence` = prop_white_comp,
                `Percent POC` = acs_nonwhite_prop,
                `White unemployment` = acs_unemploy_white,
                `Conservatism` = mrp_ideology,
                `Total population`=log_total_pop)
ms <- graph_county %>% 
  summarise(across(everything(),
                   mean)) %>% 
  pivot_longer(everything()) %>% 
  rename(Mean = value)
sds <- graph_county %>% 
  summarise(across(everything(),
                   sd)) %>% 
  pivot_longer(everything()) %>% 
  rename(`Std. Dev` = value) 
rg <- graph_county %>% 
  summarise(across(everything(),
                   range)) %>% 
  mutate(desig = c("min", "max")) %>% 
  pivot_longer(!desig) %>% 
  pivot_wider(id_cols = name, values_from=value, names_from=desig) %>% 
  mutate(Range = str_c(number(min, accuracy = .01), ", ", number(max, accuracy = .01)))
descriptives <- cbind(ms, sds %>% 
                        select(-name), 
                      rg %>% 
                        select(-name))
descriptives <- descriptives %>% 
  mutate(`M (SD)` = str_c(number(Mean, accuracy = .01), 
                          " (", 
                          number(`Std. Dev`, accuracy=.01), ")")) %>% 
  select(all_of(c("name", "M (SD)", "Range")))

cor.res <- data.frame(apa.cor.table(as.matrix(graph_county))$table.body)
cor.res <- cor.res %>% 
  filter(str_starts(Variable, "\\d+[.]")) %>% 
  mutate(name = str_remove(Variable, "\\d+[.] ")) %>% 
  left_join(descriptives, by="name") %>% 
  select(-name, -M, -SD) %>% 
  select(Variable, `M (SD)`, Range, starts_with("X")) %>% 
  rename_with(~str_remove(.x, "X"))

f <- cor.res %>% 
  flextable() 
f
write.csv(cor.res, paste0(output, "correlation_descriptives_v1.csv"))
```

Compare normality of residuals for transformed and untransformed outcome variable:

```{r}
m0.ut <- lm(prop_white_comp~acs_nonwhite_prop+mrp_ideology+log_total_pop+acs_unemploy_white,
            data=grpd_demog_county)
resid.ut <- m0.ut$residuals
m1 <- lm(sqrt_prop_white~acs_nonwhite_prop+mrp_ideology+log_total_pop+acs_unemploy_white,
            data=grpd_demog_county)
resid.m1 <- m1$residuals

resids <- data.frame(resid.ut,
                     resid.m1) %>% 
  pivot_longer(everything())

resid.plots <- resids %>%
  mutate(Outcome = recode(name, 
                       resid.m1 = "Transformed", 
                       resid.ut = "Untransformed")) %>% 
  ggplot(aes(value))+
  geom_histogram(binwidth = .1)+
  facet_wrap(vars(Outcome))+
  labs(x = "Residuals", y = "Frequency", 
       title = "Residual Distribution: Transformed vs. Untransformed Outcome")+
  theme_bw()+
  theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
        strip.text.x = element_text(size=12),
        text = element_text(family="Times"),
          axis.text=element_text(size=12),
          title = element_text(size = 10),
        legend.text = element_text(size=12))
resid.plots
#save_plot(paste0(output, "residual_comparison.png"), resid.plots)
```
```{r}
summary(m0.ut)
```



Run the regression analyses:

```{r}

m2 <- lm(prop_white_comp~acs_nonwhite_prop*mrp_ideology+acs_unemploy_white+log_total_pop,
            data=grpd_demog_county)
summary(m2)
sim_slopes(m2,pred="acs_nonwhite_prop",modx="mrp_ideology",confint=T,digits=3)
m3 <- lm(prop_white_comp~acs_nonwhite_prop*mrp_ideology*acs_unemploy_white+log_total_pop,
            data=grpd_demog_county)
summary(m3)

```
```{r}
#exploratory for review
m2a <- lm(prop_white_comp~acs_nonwhite_prop*acs_unemploy_white+mrp_ideology+log_total_pop,
            data=grpd_demog_county)
summary(m2a)
```

```{r}
#conduct slope difference tests
mrp_levels <- c((mean(grpd_demog_county$mrp_ideology,
                                                                na.rm=T)-
                                                             sd(grpd_demog_county$mrp_ideology,
                                                                na.rm = T)),
                                                          (mean(grpd_demog_county$mrp_ideology,
                                                                na.rm=T)+
                                                             sd(grpd_demog_county$mrp_ideology,
                                                                na.rm = T)))
div_levels <- c((mean(grpd_demog_county$acs_nonwhite_prop)-
                                                              sd(grpd_demog_county$acs_nonwhite_prop)),
                                                           (mean(grpd_demog_county$acs_nonwhite_prop)+
                                                              sd(grpd_demog_county$acs_nonwhite_prop)))
unemp_levels <- c((mean(grpd_demog_county$acs_unemploy_white)-
                                                              sd(grpd_demog_county$acs_unemploy_white)),
                                                           (mean(grpd_demog_county$acs_unemploy_white)+
                                                              sd(grpd_demog_county$acs_unemploy_white)))
pair.df <- data.frame()
m.lst <- lstrends(m2, ~mrp_ideology,
                  var = "acs_nonwhite_prop",at = list(mrp_ideology=mrp_levels))
print(pairs(m.lst))
tmp.pairs <- data.frame(pairs(m.lst))
tmp.pairs <- tmp.pairs %>% 
  mutate(acs_unemploy_white = NA_character_) %>% 
  select(contrast, acs_unemploy_white,estimate,SE,df,t.ratio,p.value)

# m.lst <- lstrends(m3, ~mrp_ideology_mean|acs_unemploy_white,
#                   var = "acs_nonwhite_prop",at = list(mrp_ideology_mean=mrp_levels,
#                                                       acs_unemploy_white=unemp_levels))
# print(pairs(m.lst))
# pair.df <- rbind(tmp.pairs,data.frame(pairs(m.lst)))
```


Format and save regression outputs (note that output file needs to be modified to reflect model comparison between m2 and m3, rather than m2a and m3): 

```{r}

format_regression_table <- function(models,
                                    reg_fmt = read.csv(paste0(local_data,"regression_format_v1.csv"))){
  tracker = 1
  for(m in models){
    #print(tracker)
    tmp_res = summary(m)
    tmp_coef = data.frame(tmp_res$coefficients)
    tmp_coef[,1] = number(tmp_coef[,1],accuracy = .01)#beta
    tmp_coef[,2] = number(tmp_coef[,2], accuracy = .01)#SE beta
    tmp_coef[,4] = sapply(tmp_coef[,4], statstring::format_sig_stars)#p-val
    tmp_coef[,1] = paste0(tmp_coef[,1], tmp_coef[,4])
    tmp_coef["Predictor"] = rownames(tmp_coef)
    mnum = paste0("model", tracker, "_")
    colnames(tmp_coef) = c(paste0(mnum, c("b", "se_b", "t", "p")), "Predictor")
    tmp_coef = tmp_coef %>% 
      select(Predictor, ends_with("_b"), ends_with("se_b"))
    reg_fmt = left_join(reg_fmt, tmp_coef, by = "Predictor")
    #print(number(statstring::extract_r2(m),accuracy = .001))
    reg_fmt[reg_fmt$Predictor == "R2", paste0(mnum, "se_b")] = number(tmp_res$adj.r.squared,
                                                                       accuracy = .001)
    if(tracker > 1){
      mod_aov = anova(models[[tracker - 1]], models[[tracker]])
      if(is.na(mod_aov$`Pr(>F)`[2])){ #if this is the model with the interaction btwn diversity and white unemployment, compare against model with no interactions
        mod_aov = anova(models[[1]], models[[tracker]])
        print(mod_aov)
      }
      
      reg_fmt[reg_fmt$Predictor == "Change in R2", 
              paste0(mnum, "se_b")] <- paste0(number(mod_aov$`F`[2], accuracy =.01),
                                              format_sig_stars(mod_aov$`Pr(>F)`[2]))
    }
    tracker = tracker + 1
  }
  reg_fmt[is.na(reg_fmt)] = "-"
  return(reg_fmt)
}

modlist <- list(m0.ut,m2,m2a,m3)
reg_out <- format_regression_table(modlist)
#NOTE: the output will have erroneous info for the model comparison for m3, because it is comparing m3 to m2a (rather than m3 to m2). This is changed by hand after saving the file in Excel.
write.xlsx(reg_out, paste0("outputs/", "regression_outs_no_retal_v2.xlsx"),overwrite = T)

```

```{r}
anova(m2,m3)
```



Examine the interaction:

H2: two-way between conservatism and racial diversity:


```{r}
jn_h2 <- sim_slopes(m2, pred=acs_nonwhite_prop,
                      modx=mrp_ideology,
                      modx.values = "plus-minus",
                      confint=T,jnplot=T)
jn_h2
```




```{r}
#create +/- 1 SD of mean for plots
cons_levels <- c((mean(grpd_demog_county$mrp_ideology)-
                    sd(grpd_demog_county$mrp_ideology)),
                 mean(grpd_demog_county$mrp_ideology),
                 (mean(grpd_demog_county$mrp_ideology)+
                    sd(grpd_demog_county$mrp_ideology)))
unemploy_levels <- c((mean(grpd_demog_county$acs_unemploy_white)-
                    sd(grpd_demog_county$acs_unemploy_white)),
                 mean(grpd_demog_county$acs_unemploy_white),
                 (mean(grpd_demog_county$acs_unemploy_white)+
                    sd(grpd_demog_county$acs_unemploy_white)))
div_levels <- c((mean(grpd_demog_county$acs_nonwhite_prop)-
                    sd(grpd_demog_county$acs_nonwhite_prop)),
                 mean(grpd_demog_county$acs_nonwhite_prop),
                 (mean(grpd_demog_county$acs_nonwhite_prop)+
                    sd(grpd_demog_county$acs_nonwhite_prop)))
```

Plot H1

```{r}
intrxn.sd <- effect(c("acs_nonwhite_prop"),
               mod = m0.ut)

intrxn.sd <- as.data.frame(intrxn.sd)
m0.ut <- data.frame(summary(m0.ut)$coefficients)
slope_lab <- paste0("b = ", number(m0.ut$Estimate[2],accuracy = .01),
                    format_sig_stars(m0.ut$Pr...t..[2]),
                    " SE = ", number(m0.ut$Std..Error[2],accuracy = .01))
# Plot this bad boy!
h1_plot<-
  intrxn.sd %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit))+
      geom_line(linewidth=1)+ #Can adjust the thickness of your lines
      geom_point(size=2)+ #Can adjust the size of your points
      geom_ribbon(aes(ymin=fit-se, ymax=fit+se),fill="gray",alpha=.4)+ #Can adjust your error bars
      labs(y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("Model 1: Anti-White Claim Prevalence by POC Representation")+ #Title
  theme_bw()+
  geom_text(aes(x = 25, y = 1, label=slope_lab),size=4,family="Times")+
  theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12))

save_plot(paste0(output, "h1_plot_bw.png"), h1_plot)
h1_plot
```

Plot H2: Claim prevalence by racial diversity and conservatism

```{r}

intrxn.sd <- effect(c("acs_nonwhite_prop*mrp_ideology"),
               mod = m2, 
               xlevels = list(mrp_ideology=c(cons_levels[1],cons_levels[3]),
                              acs_nonwhite_prop=c(div_levels[1],div_levels[3])))

intrxn.sd <- as.data.frame(intrxn.sd)
mod.labs <- c("-1 SD", "+ 1 SD")
# Create factors of the different variables in your interaction 
intrxn.sd$mrp_ideology<-factor(intrxn.sd$mrp_ideology,
                      levels=c(cons_levels[1],cons_levels[3]),
                      labels=c("Low Conservatism", "High Conservatism"))
intrxn.sd$mrp_ideology_rev <- factor(intrxn.sd$mrp_ideology, 
                                      levels = rev(levels(intrxn.sd$mrp_ideology)))
format_slope_text <- function(slope.df){
  new.list = rep("", nrow(slope.df))
  for(i in 1:nrow(slope.df)){
    new.list[i] = paste0("b = ", number(slope.df$`Est.`[i],
                                        accuracy = .01),
                         format_sig_stars(slope.df$p[i]),
                         " SE = ", number(slope.df$`S.E.`[i],
                                             accuracy = .01))
  }
  return(new.list)
}
m2.slopes <- jn_h2$slopes
m2.slopes["text"] <- format_slope_text(m2.slopes)

m2.slopes["x"] <- c(25, 28)
m2.slopes["y"] <- c(2,4.2)
m2.slopes["mrp_ideology"] <-c("Low Conservatism", "High Conservatism")
joined <- left_join(intrxn.sd, m2.slopes, by = "mrp_ideology")
# Plot this bad boy!
h2_plot<-
  joined %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit,
             linetype=mrp_ideology))+
      geom_line(linewidth=1, aes(linetype=mrp_ideology))+ #Can adjust the thickness of your lines
      geom_point(size=2)+ #Can adjust the size of your points
      geom_errorbar(aes(ymin=lower,ymax=upper),width=3)+
  #geom_ribbon(aes(ymin=fit-se, ymax=fit+se),fill="gray",alpha=.2)+ #Can adjust your error bars
      labs(colour = "Conservatism", linetype="Conservatism",y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("Model 2: Anti-White Claim Prevalence by\n POC Representation and Conservatism")+ #Title
  theme_bw()+
  geom_text(aes(x= x, y = y, label = text),
            family = "Times",
            size=4,
            show.legend = F)+
  theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          legend.position="top",
        legend.title = element_blank(),
        text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12),
        legend.text = element_text(size=10))
h2_plot 
save_plot(paste0("outputs/", "h2_plot_postrr.png"), h2_plot)
#save_plot("moderation_v1.png", Plot.SD)
#Plot.SD
```


```{r}
intrxn.sd <- as.data.frame(effect(c("acs_nonwhite_prop*mrp_ideology*acs_unemploy_white"),
               mod = m3, 
               xlevels = list(mrp_ideology=c(cons_levels[1],cons_levels[3]),
                              acs_unemploy_white=c(unemploy_levels[1], unemploy_levels[3]))))
mod.labs <- c("-1 SD", "+ 1 SD")
# Create factors of the different variables in your interaction 
intrxn.sd$mrp_ideology<-factor(round(intrxn.sd$mrp_ideology,2),
                      levels=c(round(cons_levels[1], 2),round(cons_levels[3],2)),
                      labels=c("Low Conservatism", "High Conservatism"))
intrxn.sd$mrp_ideology_rev <- factor(intrxn.sd$mrp_ideology, 
                                      levels = rev(levels(intrxn.sd$mrp_ideology)))

intrxn.sd$acs_unemploy_white<-factor(intrxn.sd$acs_unemploy_white,
                      levels=c(unemploy_levels[1], unemploy_levels[3]),
                      labels=c("Low White Unemployment", "High White Unemployment"))
intrxn.sd$acs_unemploy_white_rev <- factor(intrxn.sd$acs_unemploy_white, 
                                      levels = rev(levels(intrxn.sd$acs_unemploy_white)))
jn_h3 <- sim_slopes(m3, pred=acs_nonwhite_prop,
                      modx=mrp_ideology,
                      modx.values = "plus-minus",
                    mod2 = acs_unemploy_white,
                    mod2.values = "plus-minus",
                      confint=T,jnplot=T)

m3.slopes <- data.frame(jn_h3$slopes[[1]])
m3.slopes["acs_unemploy_white"] <- "Low White Unemployment"
tmp.slopes <- data.frame(jn_h3$slopes[[2]])
tmp.slopes["acs_unemploy_white"] <- "High White Unemployment"
m3.slopes <- rbind(m3.slopes, tmp.slopes)
m3.slopes["mrp_ideology"] <- c("Low Conservatism", "High Conservatism",
                                    "Low Conservatism", "High Conservatism")
m3.slopes["text"] <- format_slope_text(m3.slopes)
#low white unemploy, low cons; low white unemploy, high cons; 
#high white unemploy low cons; high white unemploy, high cons
m3.slopes["x"] <- c(55, 30,55,30)
m3.slopes["y"] <- c(2,7,2,9)

joined <- left_join(intrxn.sd, m3.slopes, by = c("mrp_ideology", "acs_unemploy_white"))
joined$acs_unemploy_white <- factor(joined$acs_unemploy_white,
                                        levels = c("Low White Unemployment","High White Unemployment"))

# Plot this bad boy!
Plot.SD<-
  joined %>% 
  ggplot(aes(x=acs_nonwhite_prop, y=fit, 
             group=mrp_ideology_rev))+
      geom_line(size=1, aes(linetype=mrp_ideology_rev))+ 
      geom_point(size=2)+ 
      facet_wrap(~acs_unemploy_white)+
      geom_ribbon(aes(ymin=fit-se, ymax=fit+se),
                  fill="gray",alpha=.2)+ 
      labs(color = "Conservatism", y = "Anti-White Claim Prevalence",
           x = "Percent POC")+
      ggtitle("Anti-White Claim Prevalence by County\nRacial Diversity, Conservatism, and White Unemployment")+ #Title
  theme_bw()+
  geom_text(aes(x= x, y = y, label = text),
            show.legend = F,family="Times",size=4)+
      theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
          legend.position="top",
        legend.title = element_blank(),
        legend.text = element_text(size=9),
        text = element_text(family="Times"),
          axis.text=element_text(size=10),
          title = element_text(size = 12),
        strip.text.x = element_text(size = 10))

save_plot(paste0(output, "h3_plot_paper_bw.png"), Plot.SD)
#save as .tiff
#save_plot(paste0(output, "h3_plot_paper_bw.tiff"), Plot.SD)
Plot.SD
```


## Robustness --- including 0 counties
Compare normality of residuals for transformed and untransformed outcome variable:

```{r}
grpd_rbst$log_total_pop <- log(grpd_rbst$total_pop)

m0.ut <- lm(prop_white_comp~acs_nonwhite_prop+mrp_ideology+log_total_pop+acs_unemploy_white,
            data=grpd_rbst)
resid.ut <- m0.ut$residuals
m1 <- lm(sqrt_prop_white~acs_nonwhite_prop+mrp_ideology+log_total_pop+acs_unemploy_white,
            data=grpd_rbst)
resid.m1 <- m1$residuals

resids <- data.frame(resid.ut,
                     resid.m1) %>% 
  pivot_longer(everything())

resid.plots <- resids %>%
  mutate(Outcome = recode(name, 
                       resid.m1 = "Transformed", 
                       resid.ut = "Untransformed")) %>% 
  ggplot(aes(value))+
  geom_histogram(binwidth = .1)+
  facet_wrap(vars(Outcome))+
  labs(x = "Residuals", y = "Frequency", 
       title = "Residual Distribution: Transformed vs. Untransformed Outcome")+
  theme_bw()+
  theme(panel.grid.major=element_blank(),
          panel.grid.minor=element_blank(),
          legend.key = element_blank(),
        strip.text.x = element_text(size=12),
        text = element_text(family="Times"),
          axis.text=element_text(size=12),
          title = element_text(size = 10),
        legend.text = element_text(size=12))
resid.plots
#save_plot(paste0(output, "residual_comparison.png"), resid.plots)
```
```{r}
summary(m0.ut)
```



Run the regression analyses:

```{r}

m2 <- lm(prop_white_comp~acs_nonwhite_prop*mrp_ideology+acs_unemploy_white+log_total_pop,
            data=grpd_rbst)
summary(m2)
sim_slopes(m2,pred="acs_nonwhite_prop",modx="mrp_ideology",confint=T,digits=3)
m3 <- lm(prop_white_comp~acs_nonwhite_prop*mrp_ideology*acs_unemploy_white+log_total_pop,
            data=grpd_rbst)
summary(m3)

```
```{r}
#exploratory for review
m2a <- lm(prop_white_comp~acs_nonwhite_prop*acs_unemploy_white+mrp_ideology+log_total_pop,
            data=grpd_rbst)
summary(m2a)
```

## Robustness: Overall unemployment

This is a robustness check testing whether overall unemployment (rather than White-specific unemployment) strengthens the amplifying effect of conservatism on the diversity-anti-White claims link.

```{r}
m1 <- lm(prop_white_comp~acs_nonwhite_prop+mrp_ideology+log_total_pop+total_unemp_rate,
            data=grpd_demog_county)
summary(m1)
m2 <- lm(prop_white_comp~acs_nonwhite_prop*mrp_ideology+total_unemp_rate+log_total_pop,
            data=grpd_demog_county)
summary(m2)
sim_slopes(m2,pred="acs_nonwhite_prop",modx="mrp_ideology",confint=T,digits=3)
m2a <- lm(prop_white_comp~acs_nonwhite_prop*total_unemp_rate+mrp_ideology+log_total_pop,
            data=grpd_demog_county)
summary(m2a)

m3 <- lm(prop_white_comp~acs_nonwhite_prop*mrp_ideology*total_unemp_rate+log_total_pop,
            data=grpd_demog_county)
summary(m3)
```

```{r}
reg_fmt_tmp <- read.csv(paste0(local_data,"regression_format_v1.csv"))
reg_fmt_tmp <- reg_fmt_tmp %>% 
  mutate(across(everything(), 
                ~str_replace_all(.x, "acs_unemploy_white", "total_unemp_rate"))) %>% 
  mutate(across(everything(), 
                ~str_replace_all(.x, "White unemployment", "All unemployment")))

modlist <- list(m1,m2,m2a,m3)
reg_out <- format_regression_table(modlist, reg_fmt=reg_fmt_tmp)

# num_line <- rep("", ncol(reg_out))
# num_line[1] <- paste0("N = ",number(nrow(grpd_demog_county), big.mark=","))
# reg_out <- rbind(reg_out, num_line)
write.xlsx(reg_out, paste0(output,
                           "robustness_all_unemploy_v2.xlsx"),overwrite = T)
```

?## Robustness: Predicting 2007-2011 claims with 2007-2011 ACS data and 2006-2011 Conservatism


```{r}
grpd.period <- read.csv(paste0(box_data, "long_annual_claims_dataset.csv"))
grpd.period <- grpd.period %>%  #filter for target years
  filter(complaint_year > 2006) %>% 
  filter(complaint_year < 2012)

grpd.period$fixed_fip <- str_pad(grpd.period$fixed_fip, width = 5, side = "left", pad="0")
grpd.wide <- grpd.period %>% 
  group_by(fixed_fip) %>% 
  summarise(n.white = sum(n.white,na.rm=T),
            n.race = sum(n.race,na.rm=T),
            n.no.retal = sum(n.no.retal, na.rm=T),
            n.complaints = sum(n.complaints, na.rm=T),
            prop.white.comp = (sum(n.white)/sum(n.no.retal))*100) %>% 
  ungroup() %>% 
  filter(fixed_fip != "FAILED")

#gather 2007-2011 ACS variables
acs.variables <- read.xlsx(paste0(box_data, "census_variable_guide.xlsx"))

old.acs <- tidycensus::get_acs(geography = "county",
                            variables = acs.variables$original_name,
                            year=2011)
old.acs.1 <- old.acs %>% 
  pivot_wider(id_cols=GEOID, names_from = variable,
              values_from = estimate) %>% 
  rename_with(~str_c(.x, "E"), .cols=-GEOID) %>% 
  select(-DP03_0009E) %>% 
  rename(DP03_0009E = DP03_0009PE)

rename.list <- acs.variables$original_name[acs.variables$original_name %in% colnames(old.acs.1)]
names(rename.list) <- acs.variables$new_name[acs.variables$original_name %in% colnames(old.acs.1)]

old.acs.1 <- old.acs.1 %>% 
  rename(!!!rename.list)
old.acs.1$fixed_fip <- old.acs.1$GEOID
old.acs.1 <- old.acs.1 %>% 
  mutate(total_white_inlf = (white_females_inlfo+
                               white_females_inlfy+
                               white_males_inlfy+
                               white_males_inlfo),
         total_white_unem = (white_females_inlf_unemy+
                               white_females_inlf_unemo+
                               white_males_inlf_unemy+
                               white_males_inlf_unemo),
         white_unemp_rate = (total_white_unem/total_white_inlf)*100,
         percent_white = (total_white/total_pop)*100,
         percent_poc = 100-percent_white)


merged.grp <- left_join(grpd.wide, old.acs.1, by = "fixed_fip")
nrow(merged.grp %>% filter(n.no.retal==0))
#2 counties had no complaints, remove them
merged.grp <- merged.grp %>% 
  filter(n.no.retal>0)

#updated ideology dataset: 
#https://dataverse.harvard.edu/file.xhtml?fileId=6690216&version=1.0
ideol <- read_dta(paste0(box_data, "aip_counties_ideology_v2022a.dta"))
ideol["fixed_fip"] <- str_pad(ideol$county_fips, width = 5, side = "left",
                                  pad = "0")
ideol <- ideol %>% 
  filter(presidential_year == 2008)

merged.grp <- left_join(merged.grp, ideol, by = "fixed_fip")
nrow(merged.grp %>% filter(is.na(mrp_ideology)))
#3 counties are missing conservatism scores--these are counties that were renamed after our study period ends (so the conservatism scores here are using a more recent Census boundary than our data)
merged.grp <- merged.grp %>% 
  filter(!is.na(mrp_ideology))

```

```{r}
merged.grp$log.total.pop <- log(merged.grp$total_pop)
```

Run models

```{r}
m1 <- lm(prop.white.comp~log.total.pop+white_unemp_rate+mrp_ideology+percent_poc, merged.grp)
summary(m1)

m2 <- lm(prop.white.comp~log.total.pop+white_unemp_rate+percent_poc*mrp_ideology, merged.grp)
summary(m2)

m2a <- lm(prop.white.comp~log.total.pop+white_unemp_rate*percent_poc+mrp_ideology, merged.grp)
summary(m2a)

m3 <- lm(prop.white.comp~log.total.pop+white_unemp_rate*percent_poc*mrp_ideology, merged.grp)
summary(m3)
```
Format outputs

```{r}
p_load(sjPlot)
tab_model(m1,m2,m2a,m3, show.se=T,show.ci=F,std.response = F)
```




